---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo=FALSE, results="hide", message=FALSE, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  results="hide",
  eval = FALSE,
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library("badger", quietly = TRUE)
```

<a href={https://github.com/Ehyaei/MPIThemes}><img src="man/figures/RTLNotes.svg" alt="RTLNotes logo" align="right" width="160" style="padding: 0 15px; float: right;"/>

# RTLNotes 

```{r, echo = FALSE, results='asis', message=FALSE,eval=TRUE}
cat(
  badger::badge_github_actions("Ehyaei/RTLNotes"),
  badger::badge_devel("Ehyaei/RTLNotes", "orange"),
  badger::badge_lifecycle("experimental"),
  badger::badge_last_commit("Ehyaei/RTLNotes")
)
```

RMarkdown enables you to write reproducible academic publications such as articles, PhD thesis, lab reports, posters, presentations, and a variety of other fascinating documents using the lightweight and plain-text Markdown syntax.

In the Rmarkdown environment, you can write text, insert images, formulas and simultaneously R and Python scripts.

> RTLNotes is not only for R users!. Python programmers can also run 
codes in Rmarkdown. This [article](https://ehyaei.github.io/MPIThemes/articles/articles/21_python_rmarkdown.html) has additional information.

When running your Rmd files with knitr, output plots, tables and code results are embedded in the md file. Then, Rstudio by using pandoc's powerful engine can convert your documents to many formats, such as PDF, Docx, HTML, epub, and... In particular, you can create PDF reports without worrying about the lateX code.

<p align="center">
<img src="man/figures/TheLordofDocuments.svg" width="100%"/>
</p>


# Features

The `RTLNotes` package contains report and presentation templates in
PDF, HTML, Office formats. 
In the articles area, you'll find an introduction to each template as well as instructions on how to config it.
The templates that have been implemented so far are as follows:

- [PDF Report (LaTeX)]()
- [Short PDF note (LaTeX)]()
- [Long Document (Gitbook/Bookdown)]()
- [Beamer Presentation (LaTeX)]()

The template' default format is based on the Maxi-Planck theme. We weren't, however, constrained by this theme. 
Reports in various styles can be created by defining the relevant parameters in YAML or templates. 
for more details see [PDF Report Template Customization](https://ehyaei.github.io/MPIThemes/articles/articles/pdf_report_template_customization.html) 

## Installation

`RTLNotes` is not (yet) available on CRAN, so install development version from GitHub 
via the `devtools` or `remotes` packages. 

``` r
# install.packages("remotes")
remotes::install_github("Ehyaei/RTLNotes")
```
For find more details of package dependencies, you can see [Get Started](https://ehyaei.github.io/RTLNotes/articles/articles/RTLNotes.html).

## Attribution

The RMarkdown packages and latex resources that inspired this effort include:

- Ahmad Ehyaei’s [MPIThemes](https://ehyaei.github.io/MPIThemes/)

