---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo=FALSE, results="hide", message=FALSE, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  results="hide",
  eval = FALSE,
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library("badger", quietly = TRUE)
```

<a href={https://github.com/Ehyaei/RTLNotes}><img src="man/figures/RTLNotes.svg" alt="RTLNotes logo" align="right" width="160" style="padding: 0 15px; float: right;"/>

# RTLNotes 

```{r, echo = FALSE, results='asis', message=FALSE,eval=TRUE}
cat(
  badger::badge_github_actions("Ehyaei/RTLNotes"),
  badger::badge_devel("Ehyaei/RTLNotes", "orange"),
  badger::badge_lifecycle("experimental"),
  badger::badge_last_commit("Ehyaei/RTLNotes")
)
```

RMarkdown enables you to write reproducible academic publications such as articles, PhD thesis, lab reports, posters, presentations, and a variety of other fascinating documents using the lightweight and plain-text Markdown syntax.
There are several packages for RMarkdown themes, but all of them are useful for left-to-right languages.
RTLNotes package tries to create a right-to-left languages theme for RMarkdown.

> RTLNotes is not only for R users!. Python programmers can also run 
codes in Rmarkdown. This [article](https://ehyaei.github.io/MPIThemes/articles/articles/21_python_rmarkdown.html) has additional information.

When running your Rmd files with knitr, output plots, tables and code results are embedded in the md file. Then, Rstudio by using pandoc's powerful engine can convert your documents to many formats, such as PDF, Docx, HTML, epub, and... In particular, you can create PDF reports without worrying about the lateX code.

<p align="center">
<img src="man/figures/TheLordofDocuments.svg" width="100%"/>
</p>


# Features

The `RTLNotes` package contains report and presentation templates in
PDF and Gitbook formats. 
In the articles section, you'll find an introduction to each template as well as instructions on how to config it.
The templates that have been implemented so far are as follows:

- [PDF Report (LaTeX)](https://ehyaei.github.io/RTLNotes/articles/articles/01_pdf_report_template_customization.html)
- [Short PDF note (LaTeX)](https://ehyaei.github.io/RTLNotes/articles/articles/02_short_pdf_report.html)
- [Long Document (Gitbook/Bookdown)](https://ehyaei.github.io/RTLNotes/articles/articles/03_bookdown_document.html)
- [Beamer Presentation (LaTeX)](https://ehyaei.github.io/RTLNotes/articles/articles/04_pdf_presentation.html)

## Installation

`RTLNotes` is not (yet) available on CRAN, so install development version from GitHub 
via the `devtools` or `remotes` packages. 


:stop_sign: :construction: Before installing the package, you should check that you have X11 plotting device, Parastoo, Vazir and Vazir-Code fonts on your machine.
The fonts source can be found [here](https://github.com/Ehyaei/RTLNotes/tree/master/inst/rmarkdown/templates/latex_report/skeleton/src/fonts).
For more details on package dependencies, see [Get Started](https://ehyaei.github.io/RTLNotes/articles/articles/RTLNotes.html). 

``` r
# install.packages("remotes")
remotes::install_github("Ehyaei/RTLNotes")
```

## Attribution

The RMarkdown packages and latex resources that inspired this effort include:

- Ahmad Ehyaei’s [MPIThemes](https://ehyaei.github.io/MPIThemes/)
- Saber Rastikerdar's [fonts](https://rastikerdar.github.io/)
