# Table

In data analysis, providing a summary of the data in the form of a table, in addition to generating a graph, is highly beneficial for expressing the results.

To generate tables, you can use a variety of R packages.
[kableExtra](https://haozhu233.github.io/kableExtra/) and [gt](https://gt.rstudio.com/) are the two main packages

## gt

To learn about the gt package features and see many examples, you can see
An informative document, [gt-cookbook](https://themockup.blog/static/gt-cookbook.html#Introduction).

```{r}
head(mtcars) %>% 
  gt(rownames_to_stub = TRUE) %>% 
  opt_row_striping() %>% 
  tab_header(
    title = "Motor Trend Car Road Tests",
    subtitle = "From the 1974 Motor Trend US magazine"
  )

```

Many features of the `gt` package can be customized, including:

-   Make changes to the table columns format, color, size and...
-   Insert row information, including names and groups.
-   Use headers, spanners, and footers to add extra information.
-   Change table style.


```{r}
gtcars %>%
    filter(ctry_origin %in% c("United States", "Japan")) %>%
    select(mfr:year, mpg_c, mpg_h, ctry_origin, msrp) %>% 
    gt(
        rowname_col = "ctry_origin",
        groupname_col = "year"
    ) %>%
    summary_rows(
        groups = TRUE,
        columns = c("msrp"),
        fns = list(Total = ~sum(.))
    ) %>%
    grand_summary_rows(
        columns = c("msrp"),
        fns = list(Overall = ~sum(.))
    ) %>% 
  data_color(
    columns = c("mpg_c", "mpg_h"),
    colors = scales::col_numeric(
      palette = c(
        "white", "green"),
      domain = c(10, 25))
  ) %>% 
  fmt_missing(
        columns = contains("mpg"),
        missing_text = ""
    )
```

## kableExtra

The `kableExtra` package is intended to enhance the basic functionality of `knitr::kable` tables.
The most impressive aspect of `kableExtra` is that the majority of its table capabilities are compatible with both HTML and PDF. It's a good choice of `kableExtra` if you can generate a PDF (LaTex) report. For more example of use this package for PDF output see this 
[manual](http://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf).
Below, there are some examples from kableExtra documents that are shown.
strongly recommends using the `booktabs = T` option for pdf output.
In the HTML manual, this option is removed.

```{r}
dt <- mtcars[1:5, 1:6]
dt %>% 
kbl() %>%
    kable_material(c("striped", "hover"))
```

```{r}
mtcars[1:8, 1:8] %>%
  kbl() %>%
  kable_paper(full_width = F) %>%
  column_spec(2, color = spec_color(mtcars$mpg[1:8]),
              link = "https://haozhu233.github.io/kableExtra/") %>%
  column_spec(6, color = "white",
              background = spec_color(mtcars$drat[1:8], end = 0.7),
              popover = paste("am:", mtcars$am[1:8]))
```

```{r}
mpg_list <- split(mtcars$mpg, mtcars$cyl)
disp_list <- split(mtcars$disp, mtcars$cyl)
inline_plot <- data.frame(cyl = c(4, 6, 8), mpg_box = "", mpg_hist = "",
                          mpg_line1 = "", mpg_line2 = "",
                          mpg_points1 = "", mpg_points2 = "", mpg_poly = "")
inline_plot %>%
  kbl(booktabs = TRUE) %>%
  kable_paper(full_width = FALSE) %>%
  column_spec(2, image = spec_boxplot(mpg_list)) %>%
  column_spec(3, image = spec_hist(mpg_list)) %>%
  column_spec(4, image = spec_plot(mpg_list, same_lim = TRUE)) %>%
  column_spec(5, image = spec_plot(mpg_list, same_lim = FALSE)) %>%
  column_spec(6, image = spec_plot(mpg_list, type = "p")) %>%
  column_spec(7, image = spec_plot(mpg_list, disp_list, type = "p")) %>%
  column_spec(8, image = spec_plot(mpg_list, polymin = 5))
```
